---
title: "Untitled"
output: html_document
date: "2025-12-08"
---

# Package loading

```{r}
rm(list = ls())

if (!require("pacman")){
  install.packages("pacman", repos='http://cran.us.r-project.org')
}

p_load(
  "tidyverse", "here", "haven", "stringr", "dplyr", "labelled",
  "gtsummary", "gt", "survey", "flextable", "officer"
)

```



# Load the datasets

```{r}
source(here::here("0_paths_jl.R"))


dt_tab1_age70 <- readRDS(here(
  path_to_data,
  "dt_tab1_age70.rds"
))

```




# Table 1

## Variable preparation
```{r}
#load function to factor variables
source(here::here("function_jl.R"))

#convert variable type to factor
dt_tab1_age70_f <- dt_tab1_age70 %>%
  recode_for_gtsum(dataset_name = "dt_tab1_age70") 

#set label
dt_tab1_age70_f<-dt_tab1_age70_f%>%
  set_variable_labels(mage="Age in 2010",
                      wave_enter="Enrollment Wave",
                      ragender_f='Gender',
                      race_ethnicity_f="Race and ethnicity",
                      raedyrs='Years of education',
                      education_degree_f="Educational attainment",
                      pedu_cat_f='Parental years of education',
                      bornsouth_f='Born in a Southern state',
                      mstat_f= 'Marital status in 2010',
                      shlt_f='Self-rated health in 2010',
                      event_type_f='End of follow-up event',
                      apoe_24_34_44_f='APOE',
                      r10smokev_f='Ever smoker in 2010',
                      r10diabe_f='Ever diabetes in 2010',
                      r10stroke_f='Ever stroke in 2010')
```



## Unweighted langaweir table 1
```{r}
langaweir_table1_data<-dt_tab1_age70_f%>%
  filter(algorithm=="lw")%>%
  select(mage,wave_enter,ragender_f,race_ethnicity_f,raedyrs,education_degree_f,pedu_cat_f,bornsouth_f,mstat_f,shlt_f,dem2010_f,hhidpn,mwgtr,stratum,secu,dem_3lw2010_f,apoe_24_34_44_f,r10smokev_f,r10diabe_f,r10stroke_f)

#Unweighted langaweir table 1
tab1_langaweir_binary <- langaweir_table1_data %>% 
  select(-hhidpn,-mwgtr, -stratum,-secu,-dem_3lw2010_f)%>%
  tbl_summary(by = dem2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_langaweir_binary


#three-category classification of cognitive status
tab1_langaweir_three <- langaweir_table1_data %>% 
  select(-hhidpn,-mwgtr, -stratum,-secu,-dem2010_f)%>%
  tbl_summary(by = dem_3lw2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_langaweir_three

```





## Weighted langaweir table 1

```{r}
#The option options(survey.lonely.psu = "adjust") is set to handle situations where a stratum contains only one PSU

options(survey.lonely.psu = "adjust")
langaweir_table1_svy <- svydesign(
  ids = ~secu,
  strata = ~stratum,
  weights = ~mwgtr,
  data = langaweir_table1_data,
  nest = TRUE
)


tab1_langaweir_svy_binary <- langaweir_table1_svy %>%
  tbl_svysummary(
    by = dem2010_f,
    include = -c(hhidpn,mwgtr, stratum,secu, dem_3lw2010_f),
    missing = "ifany",
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_langaweir_svy_binary

#three-category classification of cognitive status

tab1_langaweir_svy_three <- langaweir_table1_svy %>%
  tbl_svysummary(
    by = dem_3lw2010_f,
    include = -c(hhidpn,mwgtr, stratum,secu, dem2010_f),
    missing = "ifany",
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_langaweir_svy_three
```


## Unweighted memimp table1


```{r}
memimp_table1_data<-dt_tab1_age70_f%>%
  filter(algorithm=="wu")%>%
  select(mage,wave_enter,ragender_f,race_ethnicity_f,raedyrs,education_degree_f,pedu_cat_f,bornsouth_f,mstat_f,shlt_f,dem2010_f,hhidpn,mwgtr,stratum,secu,apoe_24_34_44_f,r10smokev_f,r10diabe_f,r10stroke_f)

tab1_memimp <- memimp_table1_data %>%
  select(-hhidpn,-mwgtr, -stratum,-secu) %>% 
  tbl_summary(by = dem2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_memimp
```


## Weighted memimp table1

```{r}
#The option options(survey.lonely.psu = "adjust") is set to handle situations where a stratum contains only one PSU
table(memimp_table1_data$stratum)

options(survey.lonely.psu = "adjust")

memimp_table1_svy <- svydesign(
  ids = ~secu,
  strata = ~stratum,
  weights = ~mwgtr,
  data = memimp_table1_data,
  nest = TRUE
)


tab1_memimp_svy <- memimp_table1_svy %>%
  tbl_svysummary(
    by = dem2010_f,
    include = -c(hhidpn,mwgtr, stratum,secu),
    missing = "ifany",
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_memimp_svy
```



## Unweighted expert table1

```{r}
dp_table1_data<-dt_tab1_age70_f%>%
  filter(algorithm=="expert")%>%
  select(mage,wave_enter,ragender_f,race_ethnicity_f,raedyrs,education_degree_f,pedu_cat_f,bornsouth_f,mstat_f,shlt_f,dem2010_f,hhidpn,mwgtr,stratum,secu,apoe_24_34_44_f,r10smokev_f,r10diabe_f,r10stroke_f) 


tab1_dp<-dp_table1_data%>% 
  select(-hhidpn,-mwgtr,-stratum,-secu)%>% 
  tbl_summary(by = dem2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_dp
```



## Weighted expert table 1

```{r}
dp_table1_svy <- svydesign(
  ids = ~secu,
  strata = ~stratum,
  weights = ~mwgtr,
  data = dp_table1_data,
  nest = TRUE
)

tab1_dp_svy <- dp_table1_svy %>%
  tbl_svysummary(
    by = dem2010_f,
    include = -c(hhidpn,mwgtr, stratum,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_dp_svy
```




## Unweighted hudomiet table 1
```{r}
hudomiet_table1_data<-dt_tab1_age70_f%>%
  filter(algorithm=="hudomiet")%>%
  select(mage,wave_enter,ragender_f,race_ethnicity_f,raedyrs,education_degree_f,pedu_cat_f,bornsouth_f,mstat_f,shlt_f,dem2010_f,hhidpn,mwgtr,secu,stratum,dem_3hudomiet2010_f,apoe_24_34_44_f,r10smokev_f,r10diabe_f,r10stroke_f) 

tab1_hudomiet_binary <- hudomiet_table1_data %>%
  select(-hhidpn,-mwgtr, -stratum,-dem_3hudomiet2010_f,-secu) %>% 
  tbl_summary(by = dem2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_hudomiet_binary

#three-category classification of cognitive status
tab1_hudomiet_three <- hudomiet_table1_data %>%
  select(-hhidpn,-mwgtr, -stratum,-dem2010_f,-secu) %>% 
  tbl_summary(by = dem_3hudomiet2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_hudomiet_three
```


## Weighted hudomiet table1

```{r}
hudomiet_table1_svy <- svydesign(
  ids = ~secu,
  strata = ~stratum,
  weights = ~mwgtr,
  data = hudomiet_table1_data,
  nest = TRUE
)

tab1_hudomiet_svy_binary <- hudomiet_table1_svy %>%
  tbl_svysummary(
    by = dem2010_f,
    include = -c(hhidpn,mwgtr, stratum,dem_3hudomiet2010_f,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_hudomiet_svy_binary

#three-category classification of cognitive status
tab1_hudomiet_svy_three <- hudomiet_table1_svy %>%
  tbl_svysummary(
    by = dem_3hudomiet2010_f,
    include = -c(hhidpn,mwgtr, stratum,dem2010_f,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_hudomiet_svy_three
```

# Table 1 Baseline cognitive status (no dementia) with end-of-follow-up events.
## unweighted langaweir_no_dem table 1

```{r}
langaweir_table1_no_dem <- dt_tab1_age70_f %>%
  filter(algorithm == "lw", dem2010_f == "No dementia in 2010") %>%
  select(mage, wave_enter, ragender_f, race_ethnicity_f, raedyrs,
         education_degree_f, pedu_cat_f, bornsouth_f, mstat_f, shlt_f,
         event_type_f, dem2010_f, hhidpn, mwgtr, stratum,secu, dem_3lw2010_f,apoe_24_34_44_f,r10smokev_f,r10diabe_f,r10stroke_f) %>%
  mutate(across(c(dem2010_f, dem_3lw2010_f), droplevels))


tab1_langaweir_no_dem_binary <- langaweir_table1_no_dem %>%
  select(-hhidpn,-mwgtr, -stratum,-dem_3lw2010_f,-secu) %>% 
  tbl_summary(by = dem2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()
  
tab1_langaweir_no_dem_binary


#three-category classification of cognitive status
tab1_langaweir_no_dem_three <- langaweir_table1_no_dem %>%
  select(-hhidpn,-mwgtr, -stratum,-dem2010_f,-secu) %>% 
  tbl_summary(by = dem_3lw2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()
  
tab1_langaweir_no_dem_three
```

## weighted langaweir_no_dem_table1
```{r}
langaweir_table1_svy_no_dem <- svydesign(
  ids = ~secu,
  strata = ~stratum,
  weights = ~mwgtr,
  data = langaweir_table1_no_dem,
  nest = TRUE
)

tab1_langaweir_svy_no_dem_binary <- langaweir_table1_svy_no_dem %>%
  tbl_svysummary(
    by = dem2010_f,
    include = -c(hhidpn,mwgtr, stratum,dem_3lw2010_f,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_langaweir_svy_no_dem_binary

#three-category classification of cognitive status
tab1_langaweir_svy_no_dem_three <- langaweir_table1_svy_no_dem %>%
  tbl_svysummary(
    by = dem_3lw2010_f,
    include = -c(hhidpn,mwgtr, stratum,dem2010_f,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_langaweir_svy_no_dem_three
```


## unweighted memimp_no_dem table 1

```{r}
memimp_table1_no_dem<-dt_tab1_age70_f%>%
  filter(algorithm=="wu", dem2010_f == "No dementia in 2010")%>%
  select(mage,wave_enter,ragender_f,race_ethnicity_f,raedyrs,education_degree_f,pedu_cat_f,bornsouth_f,mstat_f,shlt_f,event_type_f,dem2010_f,hhidpn,mwgtr,stratum,secu,apoe_24_34_44_f,r10smokev_f,r10diabe_f,r10stroke_f)%>%
  mutate(across(c(dem2010_f), droplevels))

tab1_memimp_no_dem <- memimp_table1_no_dem %>%
  select(-hhidpn,-mwgtr, -stratum,-secu) %>% 
  tbl_summary(by = dem2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_memimp_no_dem 
```

## weighted memimp_table1_no_dem
```{r}
memimp_table1_svy_no_dem <- svydesign(
  ids = ~secu,
  strata = ~stratum,
  weights = ~mwgtr,
  data = memimp_table1_no_dem,
  nest = TRUE
)

tab1_memimp_svy_no_dem <- memimp_table1_svy_no_dem %>%
  tbl_svysummary(
    by = dem2010_f,
    include = -c(hhidpn,mwgtr, stratum,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_memimp_svy_no_dem
```


## unweighted expert_table1_no_dem 

```{r}
dp_table1_no_dem <-dt_tab1_age70_f%>%
  filter(algorithm=="expert", dem2010_f == "No dementia in 2010")%>%
  select(mage,wave_enter,ragender_f,race_ethnicity_f,raedyrs,education_degree_f,pedu_cat_f,bornsouth_f,mstat_f,shlt_f,event_type_f,dem2010_f,hhidpn,mwgtr,stratum,secu,apoe_24_34_44_f,r10smokev_f,r10diabe_f,r10stroke_f)%>%
  mutate(across(c(dem2010_f), droplevels)) 

tab1_dp_no_dem <- dp_table1_no_dem %>%
  select(-hhidpn,-mwgtr, -stratum,-secu) %>% 
  tbl_summary(by = dem2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_dp_no_dem
```

## weighted expert_table1_no_dem
```{r}
dp_table1_svy_no_dem <- svydesign(
  ids = ~secu,
  strata = ~stratum,
  weights = ~mwgtr,
  data = dp_table1_no_dem,
  nest = TRUE
)

tab1_dp_svy_no_dem <- dp_table1_svy_no_dem %>%
  tbl_svysummary(
    by = dem2010_f,
    include = -c(hhidpn,mwgtr, stratum,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_dp_svy_no_dem
```


## unweighted hudomiet_table1_no_dem 
```{r}
hudomiet_table1_no_dem <- dt_tab1_age70_f %>%
  filter(algorithm == "hudomiet", dem2010_f == "No dementia in 2010") %>%
  select(mage, wave_enter, ragender_f, race_ethnicity_f, raedyrs,
         education_degree_f, pedu_cat_f, bornsouth_f, mstat_f, shlt_f,
         event_type_f, dem2010_f, hhidpn, mwgtr, stratum,secu, dem_3hudomiet2010_f,apoe_24_34_44_f,r10smokev_f,r10diabe_f,r10stroke_f) %>%
  mutate(across(c(dem2010_f, dem_3hudomiet2010_f), droplevels))


tab1_hudomiet_no_dem_binary <- hudomiet_table1_no_dem %>%
  select(-hhidpn,-mwgtr, -stratum,-dem_3hudomiet2010_f,-secu) %>% 
  tbl_summary(by = dem2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_hudomiet_no_dem_binary

#three-category classification of cognitive status
tab1_hudomiet_no_dem_three <- hudomiet_table1_no_dem %>%
  select(-hhidpn,-mwgtr, -stratum,-dem2010_f,-secu) %>% 
  tbl_summary(by = dem_3hudomiet2010_f,
              missing = "ifany", 
              missing_text="Missing",
        type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns=label, indent=0) %>%
  bold_labels()

tab1_hudomiet_no_dem_three
```

## weighted hudomiet_table1_no_dem
```{r}
hudomiet_table1_svy_no_dem <- svydesign(
  ids = ~secu,
  strata = ~stratum,
  weights = ~mwgtr,
  data = hudomiet_table1_no_dem,
  nest = TRUE
)

tab1_hudomiet_svy_no_dem_binary <- hudomiet_table1_svy_no_dem %>%
  tbl_svysummary(
    by = dem2010_f,
    include = -c(hhidpn, mwgtr, stratum, dem_3hudomiet2010_f,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_hudomiet_svy_no_dem_binary

tab1_hudomiet_svy_no_dem_three <- hudomiet_table1_svy_no_dem %>%
  tbl_svysummary(
    by = dem_3hudomiet2010_f,
    include = -c(hhidpn, mwgtr, stratum, dem2010_f,secu),
    missing = "ifany", 
    missing_text = "Missing",
    type = list(
      all_continuous() ~ "continuous",
      all_categorical() ~ "categorical"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 0
    )
  ) %>%
  add_stat_label(location = "row") %>%
  modify_column_indent(columns = label, indent = 0) %>%
  bold_labels()

tab1_hudomiet_svy_no_dem_three
```

## combine table 1s and save results
```{r}
#Combine the unweighted Table 1 results from all algorithms
merged_table_binary <- tbl_merge(
  tbls = list(tab1_langaweir_binary, tab1_hudomiet_binary, tab1_dp, tab1_memimp),
  tab_spanner = c("**Langa-Weir**", "**Hudomiet**", "**Expert Model**", "**Wu**")
)
merged_table_binary

# gtsave(
#   merged_table_binary %>% as_gt,
#   file = "D:/OneDrive - University of Southern California/R00/Manuscripts/HRS/Dementia algorithms/Output/merged_table_binary_apoe.html")


merged_table_three <- tbl_merge(
  tbls = list(tab1_langaweir_three, tab1_hudomiet_three, tab1_dp, tab1_memimp),
  tab_spanner = c("**Langa-Weir**", "**Hudomiet**", "**Expert Model**", "**Wu**")
)
merged_table_three

# gtsave(
#   merged_table_three %>% as_gt,
#   file = "D:/OneDrive - University of Southern California/R00/Manuscripts/HRS/Dementia algorithms/Output/merged_table_three_apoe.html")

#-------

#Combine the weighted Table 1 results from all algorithms
merged_table_svy_binary <- tbl_merge(
  tbls = list(tab1_langaweir_svy_binary, tab1_hudomiet_svy_binary, tab1_dp_svy, tab1_memimp_svy),
  tab_spanner = c("**Langa-Weir**", "**Hudomiet**", "**Expert Model**", "**Wu**")
)

merged_table_svy_binary


# gtsave(
#   merged_table_svy_binary %>% as_gt,
#   file = "D:/OneDrive - University of Southern California/R00/Manuscripts/HRS/Dementia algorithms/Output/merged_table_svy_binary_apoe.html")


merged_table_svy_three <- tbl_merge(
  tbls = list(tab1_langaweir_svy_three, tab1_hudomiet_svy_three, tab1_dp_svy, tab1_memimp_svy),
  tab_spanner = c("**Langa-Weir**", "**Hudomiet**", "**Expert Model**", "**Wu**")
)

merged_table_svy_three


# gtsave(
#   merged_table_svy_three %>% as_gt,
#   file = "D:/OneDrive - University of Southern California/R00/Manuscripts/HRS/Dementia algorithms/Output/merged_table_svy_three_apoe.html")

#------

#Combine the unweighted no dementia Table 1 results from all algorithms
merged_table_no_dem_binary <- tbl_merge(
  tbls = list(tab1_langaweir_no_dem_binary, tab1_hudomiet_no_dem_binary, tab1_dp_no_dem, tab1_memimp_no_dem),
  tab_spanner = c("**Langa-Weir**", "**Hudomiet**", "**Expert Model**", "**Wu**")
)

merged_table_no_dem_binary

# gtsave(
#   merged_table_no_dem_binary %>% as_gt,
#   file = "D:/OneDrive - University of Southern California/R00/Manuscripts/HRS/Dementia algorithms/Output/merged_table_no_dem_binary_apoe.html")


merged_table_no_dem_three <- tbl_merge(
  tbls = list(tab1_langaweir_no_dem_three, tab1_hudomiet_no_dem_three, tab1_dp_no_dem, tab1_memimp_no_dem),
  tab_spanner = c("**Langa-Weir**", "**Hudomiet**", "**Expert Model**", "**Wu**")
)

merged_table_no_dem_three

# gtsave(
#   merged_table_no_dem_three %>% as_gt,
#   file = "D:/OneDrive - University of Southern California/R00/Manuscripts/HRS/Dementia algorithms/Output/merged_table_no_dem_three_apoe.html")

#-------

#Combine the weighted no dementia Table 1 results from all algorithms
merged_table_svy_no_dem_binary <- tbl_merge(
  tbls = list(tab1_langaweir_svy_no_dem_binary, tab1_hudomiet_svy_no_dem_binary, tab1_dp_svy_no_dem, tab1_memimp_svy_no_dem),
  tab_spanner = c("**Langa-Weir**", "**Hudomiet**", "**Expert Model**", "**Wu**")
)

merged_table_svy_no_dem_binary

# gtsave(
#   merged_table_svy_no_dem_binary %>% as_gt,
#   file = "D:/OneDrive - University of Southern California/R00/Manuscripts/HRS/Dementia algorithms/Output/merged_table_svy_no_dem_binary_apoe.html")


merged_table_svy_no_dem_three <- tbl_merge(
  tbls = list(tab1_langaweir_svy_no_dem_three, tab1_hudomiet_svy_no_dem_three, tab1_dp_svy_no_dem, tab1_memimp_svy_no_dem),
  tab_spanner = c("**Langa-Weir**", "**Hudomiet**", "**Expert Model**", "**Wu**")
)

merged_table_svy_no_dem_three

# gtsave(
#   merged_table_svy_no_dem_three %>% as_gt,
#   file = "D:/OneDrive - University of Southern California/R00/Manuscripts/HRS/Dementia algorithms/Output/merged_table_svy_no_dem_three_apoe.html")
```




```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

